Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-20 Papers/ms.tex
Minor editing

\author[Brewer, Huijser and Lewis]{%
  Brendon~J.~Brewer$^{1}$\thanks{bj.brewer@auckland.ac.nz},
  David Huijser$^{1}$,
  Geraint F. Lewis$^2$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
  $^2$Sydney Institute for Astronomy, School of Physics, A28,
  The University of Sydney, NSW 2006, Australia}

@@

Lens modelling has been a topic of much interest over the last two decades.
Most approaches are based on Bayesian inference, maximum likelihood or
variations thereof. These approaches may be categorized according to the
following criteria:
\begin{enumerate}
\item Whether to use a simply parameterized (e.g. a Sérsic profile),
moderately flexible (e.g. a mixture model, \citet{2011MNRAS.412.2521B})
or free-form (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain
Monte Carlo with source parameters marginalized out analytically, or
with the source parameters included).
\end{enumerate}

>>>>

\author[Brewer, Huijser and Lewis]{%
  Brendon~J.~Brewer$^{1}$\thanks{To whom correspondence should be addressed. Email: {\tt bj.brewer@auckland.ac.nz}},
  David Huijser$^{1}$,
  Geraint F. Lewis$^2$
  \medskip\\
  $^1$Department of Statistics, The University of Auckland, Private Bag 92019, Auckland 1142, New Zealand\\
  $^2$Sydney Institute for Astronomy, School of Physics, A28,
  The University of Sydney, NSW 2006, Australia}

@@

Lens modelling has been a topic of much interest over the last two decades.
Most approaches are based on Bayesian inference, maximum likelihood or
variations thereof. These approaches may be categorized according to the
following criteria:
\begin{enumerate}
\item Whether to use a simply parameterized (e.g. a Sérsic profile),
moderately flexible (e.g. a mixture model, \citet{2011MNRAS.412.2521B})
or free-form (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid
[SIE]) or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain
Monte Carlo with source parameters marginalized out analytically, or
with the source parameters included).
\end{enumerate}
